\documentclass[]{config}
\usepackage{fancyhdr}
 
\pagestyle{fancy}
\fancyhf{}
 
\begin{document}

\lastupdated

\namesection{Anirudh}{Oppiliappan}{ \urlstyle{same}\href{https://icyphox.sh}{icyphox.sh} | 
\href{mailto:x@icyphox.sh}{x@icyphox.sh}
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.33\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education} 

\subsection{SRM IST}
\descript{B.Tech in Computer Science}
\location{July 2017–2021 | Chennai, IN}
\sectionsep


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     LINKS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\vspace{4mm} % Hacky fix for awkward extra vertical space

\section{Links} 
GitHub/\href{https://github.com/icyphox}{\bf icyphox} \\
LinkedIn/\href{https://www.linkedin.com/in/icyphox}{\bf icyphox} \\

\vspace{2mm} % Hacky fix for awkward extra vertical space
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     INTERESTS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Interests}
\location{Security}
\location{Privacy}
\location{Free/Libre Software}
\location{Infrastructure}
\sectionsep


\vspace{2mm} % Hacky fix for awkward extra vertical space
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Skills}
\subsection{Programming}
Python \textbullet{} C \textbullet{} Nim \textbullet{} Shell \\
\textbullet{} Go \textbullet{} Lua
\sectionsep
\subsection{Security}
Metasploit \textbullet{} Burp Suite \textbullet{}
radare2 \textbullet{} gdb
\sectionsep
\subsection{Infrastructure}
Kubernetes (GKE, bare metal) \textbullet{} Hashicorp Vault \\
\textbullet{} Prometheus  \textbullet{} Falco \\
\textbullet{} Helm
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%    TALKS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%\vspace{4mm} % Hacky fix for awkward extra vertical space
\section{Disclosures}
{\bf\location{CVE-2019-13143}} — FB50 Smart Lock

\vspace{4mm} % Hacky fix for awkward extra vertical space
\section{Talks}
{\bf\location{Cyware 2019}} — Intro to RE \\
{\bf\location{PyCon India 2019}} — "Smart lock? Nah dude."
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage} 
\hfill
\begin{minipage}[t]{0.66\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Experience}

\runsubsection{DeepSource}
\descript{Site Reliability Engineer}
\location{January 2021—Present | Bangalore, IN}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Setting up an event driven observability pipeline
\item Internal security tooling and practices (SOC2)
\item Kubernetes cluster maintenance and hardening
\item Tech: Kafka, Telegraf, InfluxDB, K8s, Tailscale, Prometheus, Falco, etc.
\end{tightemize}
\sectionsep


\runsubsection{CometChat}
\descript{Infrastructure Engineer}
\location{July 2020–December 2020 | Bangalore, IN}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Developing infrastructure and platform tooling
\item XMPP internals, websockets (RFC7395)
\item Scalable deployments of infrastructure using Docker Swarm and K8s
\item Wrote a high performance websocket proxy/relay in Nim
\end{tightemize}
\sectionsep

\runsubsection{SecureLayer7}
\descript{IoT Security Research Intern}
\location{June 2019–July 2019 | Pune, IN}
\begin{tightemize}
\item ARM, MIPS security research, exploitation
\item Firmware extraction, reverse engineering and exploitation (routers)
\item Hardware security: UART/JTAG via BusPirate, Bluetooth (BLE)
\end{tightemize}
\sectionsep

\runsubsection{Sensei Technologies}
\descript{Security Intern}
\location{May 2018–June 2018 | Bangalore, IN}
\begin{tightemize}
\item Web application security and vulnerability assesment
\item DevSecOps and automation — integrating basic web security assesment into the CI pipeline
\item Providing long-term solutions for mitigation of security threats
\end{tightemize}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     PROJECTS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{PROJECTS}

\runsubsection{shlide}
\descript{Slide deck presentation tool}
\location{Nim}
Plain-text powered, slide deck presentation tool written in pure bash. \\
\sectionsep

\runsubsection{janny}
\descript{Kubernetes resource cleaner}
\location{Python}
Clean up Kubernetes resources after a set TTL. \\
\sectionsep

\runsubsection{pwnfb50}
\descript{Exploit for CVE-2019-13143}
\location{Python}
The exploit for the FB50 smart lock. Requires only the lock's MAC address. \\
\sectionsep

\runsubsection{vite}
\descript{Minimal static site generator}
\location{Go}
A simple tool to rapidly generate static websites using only Markdown. \\
\sectionsep

\runsubsection{wsabi}
\descript{Websocket proxy}
\location{Nim}
A websocket proxy/relay that sends stats to statsd, written in Nim.
\sectionsep


\end{minipage} 
\end{document}  \documentclass[]{article}
